### 2018-11-25 Sections/protocols_for_the_quantum_internet.tex
captionspacefig

\begin{figure}[!htpb]
	\if 3\pubmode
	\includegraphics[clip=true, width=0.7\textwidth]{W_state_memory}
	\else
		\includegraphics[clip=true, width=0.475\textwidth]{W_state_memory} 
	\fi
	\caption{Quantum memory based on W-state encoding. Rails represent optical modes, and the input logical qubit state, $\ket{L}$, is represented using dual-rail encoding. The QFT fanout operation maps each of the two input basis states to one of two orthogonal $N$-qubit W-states, $\ket{W}$, differing only by their phase relationships. These are then fed into a bank of $N$ quantum memories. To readout the memories we convert back to optical encoding and decode using the inverse QFT operation. Success of the protocol is defined as there being exactly one photon between the first two `success' output modes. If a photon leaks into any of the other `failure' output modes we discard the state and assume it was erroneous. Thus error detection is heralded via the presence or absence of a photon in the `failure' modes.}\label{fig:W_state_memory}
\end{figure}

\comment{Complete}

\begin{align}
\ket\psi_L &= \alpha\ket{0}+\beta\ket{1},\nonumber\\
\alpha &= \cos \left(\frac{\theta}{2}\right),\nonumber\\
\beta &= e^{i\phi}\sin \left(\frac{\theta}{2}\right).
\end{align}

\begin{align}
P_H &=1-e^{-t/T_1} + e^{-t/T_1}(e^{-t/T_2} + \frac{2}{N}(1-e^{-t/T_2})),\nonumber\\ 
F_H &= e^{-t/T_1}\frac{e^{-t/T_2} + (1-e^{-t/T_2})\left(\frac{2+\sin^2\theta}{2N}\right)}{e^{-t/T_2}+\frac{2}{N}(1-e^{-t/T_2})}.	
\end{align}

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_prob}\\
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_fidelity}
\else
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_prob}
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_fidelity}
\fi
\caption{\comment{Get vector versions. Both 3D plots.}}\label{fig:W_state_QEC_fidelity}
\end{figure}

@@

\begin{figure}[!htpb]
	\includegraphics[clip=true, width=0.4\textwidth]{random_number_generation}
	\caption{A simple optical implementation for a quantum binary random number generator. The source prepares single photons, which pass through a polarisation filter (\textit{F}) to retain only horizontally polarised photons, $\ket{H}$. A wave-plate (\textit{WP}) then rotates the polarisation into the diagonal basis, yielding a stream of $\ket{+}$ polarised photons. These are then separated into horizontal and vertical components via a polarising beamsplitter (\textit{PBS}), each of which are independently photo-detected (\textit{D}). If correctly implemented, the two detectors click one at a time, each with 50\% probability, and the random stream is inherently non-deterministic, guaranteed by the non-determinism of quantum mechanics. Random numbers are produced at a rate of 1 bit per photo-detection.}\label{fig:random_number_generation}
\end{figure}

>>>>

\begin{figure}[!htpb]
	\if 3\pubmode
	\includegraphics[clip=true, width=0.7\textwidth]{W_state_memory}
	\else
		\includegraphics[clip=true, width=0.475\textwidth]{W_state_memory} 
	\fi
	\captionspacefig \caption{Quantum memory based on W-state encoding. Rails represent optical modes, and the input logical qubit state, $\ket{L}$, is represented using dual-rail encoding. The QFT fanout operation maps each of the two input basis states to one of two orthogonal $N$-qubit W-states, $\ket{W}$, differing only by their phase relationships. These are then fed into a bank of $N$ quantum memories. To readout the memories we convert back to optical encoding and decode using the inverse QFT operation. Success of the protocol is defined as there being exactly one photon between the first two `success' output modes. If a photon leaks into any of the other `failure' output modes we discard the state and assume it was erroneous. Thus error detection is heralded via the presence or absence of a photon in the `failure' modes.}\label{fig:W_state_memory}
\end{figure}

For a logical qubit of the form,
\begin{align}
\ket\psi_L &= \alpha\ket{0}+\beta\ket{1},\nonumber\\
\alpha &= \cos \left(\frac{\theta}{2}\right),\nonumber\\
\beta &= e^{i\phi}\sin \left(\frac{\theta}{2}\right),
\end{align}
the heralding success probability, and associated fidelity of the heralded events is given by,
\begin{align}
P_H &=1-e^{-t/T_1} + e^{-t/T_1}(e^{-t/T_2} + \frac{2}{N}(1-e^{-t/T_2})),\nonumber\\ 
F_H &= e^{-t/T_1}\frac{e^{-t/T_2} + (1-e^{-t/T_2})\left(\frac{2+\sin^2\theta}{2N}\right)}{e^{-t/T_2}+\frac{2}{N}(1-e^{-t/T_2})}.	
\end{align}

@@

\begin{figure}[!htbp]
\if 2\pubmode
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_prob}\\
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_fidelity}
\else
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_prob}
	\includegraphics[clip=true, width=0.475\textwidth]{W_state_QEC_fidelity}
\fi
\captionspacefig \caption{Heralding probability ($P_H$) and associated error-corrected fidelity ($F_H$) for a single photonic qubit stored in a W-state quantum error correction circuit with decoherence times $T_1$ (amplitude damping)\index{Amplitude damping} and $T_2$ (dephasing)\index{Dephasing}\index{T$_1$-time}\index{T$_2$-time}. We have chosen \mbox{$\theta=0$} (representing worst-case behaviour), storage time \mbox{$t=1$}, and several levels of encoding $N$.}\label{fig:W_state_QEC_fidelity}
\end{figure}

@@

\begin{figure}[!htpb]
	\includegraphics[clip=true, width=0.4\textwidth]{random_number_generation}
	\captionspacefig \caption{A simple optical implementation for a quantum binary random number generator. The source prepares single photons, which pass through a polarisation filter (\textit{F}) to retain only horizontally polarised photons, $\ket{H}$. A wave-plate (\textit{WP}) then rotates the polarisation into the diagonal basis, yielding a stream of $\ket{+}$ polarised photons. These are then separated into horizontal and vertical components via a polarising beamsplitter (\textit{PBS}), each of which are independently photo-detected (\textit{D}). If correctly implemented, the two detectors click one at a time, each with 50\% probability, and the random stream is inherently non-deterministic, guaranteed by the non-determinism of quantum mechanics. Random numbers are produced at a rate of 1 bit per photo-detection.}\label{fig:random_number_generation}
\end{figure}

### 2018-11-25 Sections/quantum_algorithms.tex
Fig resize
Qubus arch sec
captionspacefig

\begin{figure}[!htbp]
\includegraphics[clip=true,width=0.4\textwidth]{oracle_circuits}
\caption{Simple example of the progression of turning a classical function into a quantum oracle. (a) A simple classical circuit, the XOR gate, which is not invertible, implementing 2-bit modulo 2 addition. (b) By introducing an ancillary bit we are able to make a reversible implementation of the same circuit. (c) With a reversible circuit construction, we can directly substitute the reversible gates for their unitary equivalents, yielding a quantum oracle implementation of the starting function.}\label{fig:oracle_circ}	
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QFT($\ket{x}$):
\begin{enumerate}
\item Apply the recursively-defined circuit below to the $n$-qubit input state $\ket{x}$, where,
\begin{align}
\hat{R}_\theta=\left(\begin{matrix}
1 & 0 \\
0 & e^{i\theta}	
\end{matrix}\right),
\end{align}
is a generalised phase-flip gate.
\item The amplitudes in the $n$-qubit output state $\ket{y}$ are given by the quantum Fourier transform of the input amplitudes, implementing the transformation,
\begin{align}
	\hat{\mathrm{QFT}} \ket{j} \to \frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \omega^{jk}\ket{k},
\end{align}
on the logical basis states, or in matrix form,
\begin{align}
\frac{1}{\sqrt{N}} \left(\begin{matrix}
  1 & 1 & 1 & \dots & 1\\
  1 & \omega & \omega^2 & \dots & \omega^{N-1} \\
  1 & \omega^2 & \omega^4 & \dots & \omega^{2(N-1)} \\
  \vdots & \vdots & \vdots & \ddots & \vdots \\
  1 & \omega^{N-1} & \omega^{2(N-1)} &\dots &\omega^{(N-1)(N-1)}
\end{matrix}\right),
\end{align}
where there are,
\begin{align}
N=2^n,
\end{align}
logical basis states.
\item The quantum circuit requires $O(n^2)$ gates.
\item Return $\ket{y}$.
\item $\Box$
\end{enumerate}
\includegraphics[width=\textwidth]{QFT}
}
\end{mdframed}
\captionspacealg \caption{The quantum Fourier transform (QFT) algorithm. The circuit is defined recursively, defining the $n$-qubit QFT in terms of an \mbox{$n-1$}-qubit QFT.} \label{alg:QFT}\index{Quantum Fourier transform}
\end{table}

@@

Shor's algorithm works by first reducing integer factorisation to another problem, \textit{period finding}\index{Period finding}. For the function,
\begin{align}
f(x)= a^x \,\mathrm{mod}\, N,	
\end{align}
find its period \mbox{$r\in\mathbb{Z}^+$}, the smallest integer such that,
\begin{align}
f(x)=f(x+r) \,\mathrm{mod} N.	
\end{align}
With the ability to solve the period finding problem, an efficient classical algorithm exists for transforming this solution to a solution for factoring.

The algorithm derives its power from a quantum Fourier transform subroutine (Sec.~\ref{sec:QFT_alg}), and has runtime,
\begin{align}
O((\log N)^2(\log\log N)(\log\log\log N)),	
\end{align}
making it quantum-efficient. By contrast, the best-known classical algorithm, the \textit{general number field sieve}\index{General number field sieve}, requires time,
\begin{align}
	O(e^{1.9(\log N)^{\frac{1}{3}}(\log\log N)^\frac{2}{3}}).
\end{align}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Shor(a,N):
\begin{enumerate}
	\item For function,
	\begin{align}
		f(x)= a^x \,\mathrm{mod}\, N,	
	\end{align}
	we wish to find the smallest integer $r$ such that,
	\begin{align}
		f(x)=f(x+r) \,\mathrm{mod} \,N.	
	\end{align}
	\item Run the circuit below.
	\item Efficient classical processing of the measured output registers reveals $r$ with high probabiliy.
	\item Classically verify that,
	\begin{align}
		f(x)=f(x+r) \,\mathrm{mod} \,N.	
	\end{align}
	\item If it isn't then repeat the circuit to obtain more samples. 
    \item $\Box$
\end{enumerate}
\includegraphics[width=\textwidth]{shor_circuit}
}
\end{mdframed}
\captionspacealg \caption{Shor's quantum algorithm for integer factorisation.} \label{alg:shor}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.4\textwidth]{shallow_circuits_2D}
\caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid. The qubits are represented as green circles (some omitted for clarity), and CZ gates are drawn in red.\comment{Better explanation}}
\end{figure}

>>>>

\begin{figure}[!htbp]
\includegraphics[clip=true,width=0.4\textwidth]{oracle_circuits}
\captionspacefig \caption{Simple example of the progression of turning a classical function into a quantum oracle. (a) A simple classical circuit, the XOR gate, which is not invertible, implementing 2-bit modulo 2 addition. (b) By introducing an ancillary bit we are able to make a reversible implementation of the same circuit. (c) With a reversible circuit construction, we can directly substitute the reversible gates for their unitary equivalents, yielding a quantum oracle implementation of the starting function.}\label{fig:oracle_circ}	
\end{figure}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function QFT($\ket{x}$):
\begin{enumerate}
\item Apply the recursively-defined circuit below to the $n$-qubit input state $\ket{x}$, where,
\begin{align}
\hat{R}_\theta=\left(\begin{matrix}
1 & 0 \\
0 & e^{i\theta}	
\end{matrix}\right),
\end{align}
is a generalised phase-flip gate.
\item The amplitudes in the $n$-qubit output state $\ket{y}$ are given by the quantum Fourier transform of the input amplitudes, implementing the transformation,
\begin{align}
	\hat{\mathrm{QFT}} \ket{j} \to \frac{1}{\sqrt{N}}\sum_{k=0}^{N-1} \omega^{jk}\ket{k},
\end{align}
on the logical basis states, or in matrix form,
\begin{align}
\frac{1}{\sqrt{N}} \left(\begin{matrix}
  1 & 1 & 1 & \dots & 1\\
  1 & \omega & \omega^2 & \dots & \omega^{N-1} \\
  1 & \omega^2 & \omega^4 & \dots & \omega^{2(N-1)} \\
  \vdots & \vdots & \vdots & \ddots & \vdots \\
  1 & \omega^{N-1} & \omega^{2(N-1)} &\dots &\omega^{(N-1)(N-1)}
\end{matrix}\right),
\end{align}
where there are,
\begin{align}
N=2^n,
\end{align}
logical basis states.
\item The quantum circuit requires $O(n^2)$ gates.
\item Return $\ket{y}$.
\item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
\includegraphics[width=\textwidth]{QFT}
\else
\includegraphics[width=0.75\textwidth]{QFT}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{The quantum Fourier transform (QFT) algorithm. The circuit is defined recursively, defining the $n$-qubit QFT in terms of an \mbox{$n-1$}-qubit QFT.} \label{alg:QFT}\index{Quantum Fourier transform}
\end{table}

@@

Shor's algorithm works by first reducing integer factorisation to another problem, \textit{period finding}\index{Period finding}. For the function,
\begin{align}
f(x)= a^x \,\mathrm{mod}\, N,	
\end{align}
find its period \mbox{$r\in\mathbb{Z}^+$}, the smallest integer such that,
\begin{align}
f(x)=f(x+r) \,\mathrm{mod}\, N.	
\end{align}
With the ability to solve the period finding problem, an efficient classical algorithm exists for transforming this solution to a solution for factoring.

The algorithm derives its power from a quantum Fourier transform subroutine (Sec.~\ref{sec:QFT_alg}), and has runtime,
\begin{align}
O((\log N)^2(\log\log N)(\log\log\log N)),	
\end{align}
making it quantum-efficient. By contrast, the best-known classical algorithm, the \textit{general number field sieve}\index{General number field sieve}, requires time,
\begin{align}
	O\left((e^{1.9(\log N)^{\frac{1}{3}}(\log\log N)^\frac{2}{3}}\right).
\end{align}

@@

\begin{table}[!htbp]
\begin{mdframed}[innertopmargin=3pt, innerbottommargin=3pt, nobreak]
\texttt{
function Shor(a,N):
\begin{enumerate}
	\item For function,
	\begin{align}
		f(x)= a^x \,\mathrm{mod}\, N,	
	\end{align}
	we wish to find the smallest integer $r$ such that,
	\begin{align}
		f(x)=f(x+r) \,\mathrm{mod} \,N.	
	\end{align}
	\item Run the circuit below.
	\item Efficient classical processing of the measured output registers reveals $r$ with high probabiliy.
	\item Classically verify that,
	\begin{align}
		f(x)=f(x+r) \,\mathrm{mod} \,N.	
	\end{align}
	\item If it isn't then repeat the circuit to obtain more samples. 
    \item $\Box$
\end{enumerate}
\begin{center}
\if 2\pubmode
\includegraphics[width=\textwidth]{shor_circuit}
\else
\includegraphics[width=0.55\textwidth]{shor_circuit}
\fi
\end{center}
}
\end{mdframed}
\captionspacealg \caption{Shor's quantum algorithm for integer factorisation.} \label{alg:shor}
\end{table}

@@

\begin{figure}[!htbp]
\includegraphics[clip=true, width=0.35\textwidth]{shallow_circuits_2D}
\captionspacefig \caption{\label{fig:2DHLFgrid} Implementation of the HLF problem on a 2D grid. The qubits are represented as green circles (some omitted for clarity), and CZ gates are drawn in red.\comment{Better explanation}}
\end{figure}

### 2018-11-25 Sections/the_quantum_sneakernet.tex
captionspacefig

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.7\textwidth]{sneakernet_boat}
\else
\includegraphics[clip=true, width=0.475\textwidth]{sneakernet_boat}
\fi
\caption{In the quantum Sneakernet\texttrademark entanglement distribution protocol, rather than using conventional flying qubits, we take highly error-corrected stationary qubits and physically transport them over long distances as freight. The error correction must be sufficient to maintain coherence over the time-scale of the journey, which could be anything from hours (when flying) to weeks (by sea\footnote{Or indefinitely if the destination is Australia and you're fleeing war crimes.}). The mode of transport only transports one half of an error-corrected Bell pair, transferring the initial entanglement between source and vessel, $\ket{\Psi^+}_{A,B}$, to be between source and destination, $\ket{\Psi^+}_{A,C}$. Because all Bell pairs are identical and infinitely reproducible, latency presents no problem. For example, when using a Bell pair to teleport a qubit over long distances, when the Bell pair arrives is unimportant, as long as it's available at the time of teleportation. Thus, our Bell pair cargo carriers can simply operate in the background, transporting Bell pairs with as much bandwidth as possible, which may then be buffered by the recipient until required, latency being unimportant provided the coherence lifetime of the error correcting code is long enough.}\label{fig:sneakernet_boat}	
\end{figure}

>>>>

\begin{figure}[!htbp]
\if 3\pubmode
\includegraphics[clip=true, width=0.7\textwidth]{sneakernet_boat}
\else
\includegraphics[clip=true, width=0.475\textwidth]{sneakernet_boat}
\fi
\captionspacefig \caption{In the quantum Sneakernet\texttrademark entanglement distribution protocol, rather than using conventional flying qubits, we take highly error-corrected stationary qubits and physically transport them over long distances as freight. The error correction must be sufficient to maintain coherence over the time-scale of the journey, which could be anything from hours (when flying) to weeks (by sea\footnote{Or indefinitely if the destination is Australia and you're fleeing war crimes.}). The mode of transport only transports one half of an error-corrected Bell pair, transferring the initial entanglement between source and vessel, $\ket{\Psi^+}_{A,B}$, to be between source and destination, $\ket{\Psi^+}_{A,C}$. Because all Bell pairs are identical and infinitely reproducible, latency presents no problem. For example, when using a Bell pair to teleport a qubit over long distances, when the Bell pair arrives is unimportant, as long as it's available at the time of teleportation. Thus, our Bell pair cargo carriers can simply operate in the background, transporting Bell pairs with as much bandwidth as possible, which may then be buffered by the recipient until required, latency being unimportant provided the coherence lifetime of the error correcting code is long enough.}\label{fig:sneakernet_boat}	
\end{figure}
